### 2024-06-03 thesis/input_files/paper1.tex
final

\section{Kernel families}\label{kernel families}
The selection of the kernel determines the class of functions that will be searched by the learning algorithm. Prior knowledge of the problem domain can help restricting the candidate families of kernel functions. 
Table \ref{tab:kernel types} contains popular kernel families in literature and applications.
\begin{table}
    \caption{Kernel types}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{lll}
        \toprule
       Kernel function & Equation & Hyperparameters \\
       \midrule
       Linear &  $k(x,y)=x^\intercal y$ &   \\
       Polynomial &  $k(x,y)=(x^\intercal y+c)^d$ &   c, d\\
       Gaussian RBF &  $k(x,y)=\exp\left(-\frac{\|x-y\|_{2}^2}{2\l^2}\right)$ &   $l$\\
       Exponential RBF/Laplacian& $k(x,y)=\exp\left(-\frac{\|x-y\|_{2}}{l}\right)$ &   $l$\\
       Absolute Laplacian& $k(x,y)=\exp\left(-\frac{\|x-y\|_{1}}{l}\right)$ &   $l$\\
       Hyperbolic/Sigmoid Kernel &  $k(x,y2)=\tanh(\gamma x^\intercal y+r)$ &  $\gamma$, r \\
       Periodic &  $k(x,y)=\exp\left(\frac{-2 sin^2\left(\frac{\pi}{p}\|x-y\|_{2} \right)}{l^2}\right) $ &   $p, l$\\
       Chi-squared kernel &  $k(x,y)=\exp\left(-\gamma \sum\limits_i \frac{(x_i - y_i)^2}{x_i+y_i}\right) $ &   $\gamma$\\
        Cosine  &  $k(x,y)=\frac{x^\intercal y}{\|x\|_{2}\|y\|_{2}}$ &   \\
       Matérn  &  $k(x, y) =  \frac{1}{\Gamma(\nu)2^{\nu-1}}\Bigg(
        \frac{\sqrt{2\nu}}{l} \|x-y|\|_{2}
        \Bigg)^\nu Y_\nu\Bigg(
        \frac{\sqrt{2\nu}}{l} \|x-y|\|_{2}\Bigg)$ &  $l, \nu$ \\

@@

Notice, in the Matérn family, $\Gamma(\cdot)$ is the gamma function while $Y(\cdot)$ is the Bessel function of the second kind.
\\
When $\nu=p+\frac{1}{2}$, $p \in \mathbb{N}^+$, the Matérn kernel can be rewritten as a product of an exponential and a polynomial of degree $p$. 
\\
$$k(x,y)=\exp \left(-{\frac {{\sqrt {2p+1}}\|x-y|\|_{2}}{l }}\right){\frac {p!}{(2p)!}}\sum\limits_{i=0}^{p}{\frac {(p+i)!}{i!(p-i)!}}\left({\frac {2{\sqrt {2p+1}}\|x-y|\|_{2}}{l }}\right)^{p-i}$$
\\
For example:
\begin{itemize}
    \item $p=0,\nu=\frac{1}{2} \implies k(x,y)=\exp\left(-\frac{\|x-y\|_{2}}{l}\right)$
    \item $p=1,\nu=\frac{3}{2} \implies 
    k(x,y)=\left(1+{\frac {{\sqrt {3}}\|x-y\|_{2}}{l }}\right)\exp \left(-{\frac {{\sqrt {3}}\|x-y\|_{2}}{l }}\right)$
    \item $p=2,\nu=\frac{5}{2} \implies k(x,y)=\left(1+{\frac {{\sqrt {5}}\|x-y\|_{2}}{l }}+{\frac {5\|x-y\|_{2}^{2}}{3 l ^{2}}}\right)\exp \left(-{\frac {{\sqrt {5}}\|x-y\|_{2}}{l }}\right)$
\end{itemize}

When $\nu=\frac{1}{2}$ the Matérn kernel corresponds to the Laplacian kernel. If the predictors are one dimensional, then the Absolute Laplacian and the Matern 0.5 are equivalent. %L2 norm=L1 norm
Furthermore, as $\nu \to \infty$ we have that the Matérn kernel converges to the Gaussian RBF kernel.
$k(x,y)=\exp\left(\frac{-\|x-y\|_{2}^2}{2l^2}\right)$

>>>>

\section{Kernel families}\label{kernel families}
The selection of the kernel determines the class of functions that will be searched by the learning algorithm. Prior knowledge of the problem domain can help restricting the candidate families of kernel functions.
Table \ref{tab:kernel types} contains popular kernel families in literature and applications.
\begin{table}
    \caption{Kernel types}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{lll}
        \toprule
       Kernel function & Equation & Hyperparameters \\
       \midrule
       Linear &  $k(x,y)=x^\intercal y$ &   \\
       Polynomial &  $k(x,y)=(x^\intercal y+c)^d$ &   c, d\\
       Gaussian RBF &  $k(x,y)=\exp\left(-\frac{\|x-y\|_{2}^2}{2\l^2}\right)$ &   $l$\\
       Exponential RBF/Laplacian& $k(x,y)=\exp\left(-\frac{\|x-y\|_{2}}{l}\right)$ &   $l$\\
       Absolute Laplacian& $k(x,y)=\exp\left(-\frac{\|x-y\|_{1}}{l}\right)$ &   $l$\\
       Hyperbolic/Sigmoid Kernel &  $k(x,y2)=\tanh(\gamma x^\intercal y+r)$ &  $\gamma$, r \\
       Periodic &  $k(x,y)=\exp\left(\frac{-2 sin^2\left(\frac{\pi}{p}\|x-y\|_{2} \right)}{l^2}\right) $ &   $p, l$\\
       Chi-squared kernel &  $k(x,y)=\exp\left(-\gamma \sum\limits_i \frac{(x_i - y_i)^2}{x_i+y_i}\right) $ &   $\gamma$\\
        Cosine  &  $k(x,y)=\frac{x^\intercal y}{\|x\|_{2}\|y\|_{2}}$ &   \\
       Matern  &  $k(x, y) =  \frac{1}{\Gamma(\nu)2^{\nu-1}}\Bigg(
        \frac{\sqrt{2\nu}}{l} \|x-y|\|_{2}
        \Bigg)^\nu Y_\nu\Bigg(
        \frac{\sqrt{2\nu}}{l} \|x-y|\|_{2}\Bigg)$ &  $l, \nu$ \\

@@

Notice, in the Matern family, $\Gamma(\cdot)$ is the gamma function while $Y(\cdot)$ is the Bessel function of the second kind.
\\
When $\nu=p+\frac{1}{2}$, $p \in \mathbb{N}$, the Matern kernel can be rewritten as a product of an exponential and a polynomial of degree $p$. 
\\
$$k(x,y)=\exp \left(-{\frac {{\sqrt {2p+1}}\|x-y|\|_{2}}{l }}\right){\frac {p!}{(2p)!}}\sum\limits_{i=0}^{p}{\frac {(p+i)!}{i!(p-i)!}}\left({\frac {2{\sqrt {2p+1}}\|x-y|\|_{2}}{l }}\right)^{p-i}$$
\\
For example:
\begin{itemize}
    \item $p=0,\nu=\frac{1}{2} \implies k(x,y)=\exp\left(-\frac{\|x-y\|_{2}}{l}\right)$
    \item $p=1,\nu=\frac{3}{2} \implies 
    k(x,y)=\left(1+{\frac {{\sqrt {3}}\|x-y\|_{2}}{l }}\right)\exp \left(-{\frac {{\sqrt {3}}\|x-y\|_{2}}{l }}\right)$
    \item $p=2,\nu=\frac{5}{2} \implies k(x,y)=\left(1+{\frac {{\sqrt {5}}\|x-y\|_{2}}{l }}+{\frac {5\|x-y\|_{2}^{2}}{3 l ^{2}}}\right)\exp \left(-{\frac {{\sqrt {5}}\|x-y\|_{2}}{l }}\right)$
\end{itemize}

When $\nu=\frac{1}{2}$ the Matern kernel corresponds to the Laplacian kernel. If the predictors are one dimensional, then the Absolute Laplacian and the Matern 0.5 are equivalent. %L2 norm=L1 norm
Furthermore, as $\nu \to \infty$ we have that the Matern kernel converges to the Gaussian RBF kernel.
$k(x,y)=\exp\left(\frac{-\|x-y\|_{2}^2}{2l^2}\right)$

### 2024-06-03 thesis/input_files/point.tex
final

\subsection{Autoregressive integrated moving average with exogenous variables}
The ARIMAX model adds explanatory variables to ARIMA. Hence, we have
\begin{equation}
    \hat{y}_n=\sum\limits_{k=1}^{h} \mu_i X_{n-k}+\sum\limits_{i=1}^{p}\psi_i y_{n-i}^{(d)}+\sum\limits_{j=1}^{q}\theta_j \epsilon_{n-j}+ \epsilon_{n}
\end{equation}
\subsection{Seasonal autoregressive integrated moving average and seasonal autoregressive integrated moving average with exogenous variables}
SARIMA and SARIMAX incorporate seasonalities into time series models. The notation for these models is ARIMA$(p,d,q)(P,D,Q)_m$. The second term $(P,D,Q)_m$ represents the autoregressive structure of the seasonal pattern, where $m$ indicates the number of seasonalities of the time series.
For instance, in modelling series of hourly data with daily periodicity, we would set $m=24$.
Writing SARIMA in compact notation we have
\\
\begin{equation}
    \psi(B)\Psi(B^P)\nabla^d\nabla_m^Dy_t=\theta(B)\Theta(B^Q)\epsilon_t
\end{equation}
where $\Psi$ and $\Theta$ account for the $P$ and $Q$ of the seasonal pattern $m$ respectively.
\section{Generalized additive model}
% in standard regression the predicted y are normal since error are normal. But if we want to model say a y bernoulli which is the rate of success we can link the domain of bernoulli to that of gaussian with a link function
Generalized additive models (GAMs) take the form
\begin{equation}
    g[\mathbb{E}(Y_i)]=\alpha+f_1(X_1)+\dots+f_p(X_p)
\end{equation}
$f_i$ are smooth functions which are fitted using cubic smoothing splines.
Herein, $g$ is called link function and characterizes the specific GAM model \cite{hastie2017generalized}. Approximations for $f_i$ are obtained through an iterative procedure, the backfitting algorithm.

%prophet meta
Particularly successful in time series forecasting is the Prophet model \cite{taylor2018forecasting}, developed by Meta. This additive model is capable of handling non linear trends, holiday effects and yearly weekly, and daily seasonalities. This is, the reason why we choose it as a benchmark to compare against.
\section{K-nearest neighbours regression}
K-nearest neighbours regression forecasts by averaging the most similar $k$ instances in the training set \cite{macqueen1967some}. $k$ is the algorithm hyperparameter, it stands for the number of neighbours; a small $k$ leads to overfitting while a big $k$ leads to underfitting. 
Since it is a metric based algorithm, it is important to normalize data in order to give equal weights to features with different scales, see Appendix \ref{appendix:normalization}.
This algorithm is made up of two decisions: first, the choice of the metric and second, the method for combining targets.

@@

\section{Artificial neural networks}
Artificial neural networks (ANN) have been successfully applied in the context of electricity markets forecasting. The basic building block of this class of methods is the perceptron \cite{rosenblatt1958perceptron}.
This model is defined as follows
\begin{equation}
    y=\psi(wx+b)
\end{equation}
where $\psi$ is an activation function and $w,b$ are the parameters of the neuron. The parameters are typically optimized through gradient descent.

@@

\section{Kernel methods}
\subsection{Kernel ridge regression}
In the setting of kernel ridge regression, we aim at estimating $f$ such that $y=f(x)+\epsilon$. Given an RKHS $\mathcal{H}$, we can estimate $f$ by solving the optmisation problem
\begin{equation}\label{eq:kernel ridge}
    \hat{f}=\argmin{f\in \mathcal{H}}\frac{1}{2}\sum\limits_{i=1}^n(y_i-f(x_i))^2+\frac{\tau}{2}\|f\|_{\mathcal{H}}^2
\end{equation}
Before proceeding, we need to introduce the representer theorem.
\begin{theorem}
    Let $k:\mathcal{X} \times \mathcal{X} \to \mathbb{R}$ on a non empty set $\mathcal{X}$ with corresponding RKHS $\mathcal{H}$,
    a strictly increasing real valued function $g:[0,\infty) \to \mathbb{R}$, and the loss function $E:(\mathcal{X}\times \mathbb{R}^2)^n \to \mathbb{R} \cup \{\infty\}$.
    Consider the regularised risk functional $Risk[f]:f \mapsto  E\left((x_{1},y_{1},f(x_{1})),\ldots, (x_{n},y_{n},f(x_{n}))\right)+g\left(\| f\|_{\mathcal{H}} \right)$. Then any minimizer of the empirical risk can be represented as $$ f^{*}(\cdot )=\sum\limits_{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})$$
\end{theorem}

\begin{proof}
    By orthogonal projection, any $f \in \mathcal{H}$ can be decomposed as the sum of two functions, with the first lying in the $\textrm{span}\{\phi(x_1),\dots, \phi(x_n)\}$ and the second staying in the orthogonal complement of the former. Letting $\nu$ denote a function from the orthogonal complement, we have
    \begin{equation}
        f=\sum\limits_{i=1}^{n}\alpha_i \phi(x_i)+\nu
    \end{equation}
    Applying $f$ to any point, by the reproducing property we have
    \begin{equation}
        \begin{aligned}
            f(x_j)=&\langle \phi(x_j), \sum\limits_{i=1}^{n}\alpha_i \phi(x_i)+\nu\rangle_{\mathcal{H}}
            \\
            =&\sum\limits_{i=1}^{n}\alpha_i\langle \phi(x_j), \phi(x_i)\rangle_{\mathcal{H}}
        \end{aligned}
    \end{equation}
    This means that setting $\nu=0$ does not affect the evaluation of $f$.
    Next consider the regularisation term. The functional $g$ is defined to be strictly monotonic in order to penalise more complex functions $f$.
    \begin{equation}
        \begin{aligned}
            g(\|f\|_{\mathcal{H}})=&g\left(\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)+v\right\|_\mathcal{H}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)+v\right\|_\mathcal{H}^2}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2+\left\|v\right\|_\mathcal{H}^2+2\left\langle\sum\limits_{i=1}^n \alpha_i \phi(x_i),\nu \right\rangle_{\mathcal{H}}}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2+\|v\|_\mathcal{H}^2}\right)
            \\
            \geq &g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2}\right)
        \end{aligned}
    \end{equation}
    Hence, we can conclude that setting $\nu=0$ decreases the second term while the first term is not affected. Thus, it follows that any minimizer of the risk functional of Equation \ref{eq:kernel ridge} must be of the following form
    \begin{equation}
        f^*(\cdot)=\sum\limits_{i=1}^n \alpha_i \phi(x_i)=\sum\limits_{i=1}^n \alpha_i k(\cdot, x_i)
    \end{equation}
\end{proof}

Employing the representer theorem, we can rewrite Equation \ref{eq:kernel ridge} in matrix notation as
\begin{equation}
    \begin{aligned}
    \hat{\alpha}=&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2}\left\|\sum _{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})\right\|_{\mathcal{H}}^2
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \left\langle \sum _{i=1}^{n}\alpha _{i}k(\cdot ,x_{i}),\sum _{j=1}^{n}\alpha _{j}k(\cdot ,x_{j})\right\rangle_{\mathcal{H}}^2
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \sum _{i,j=1}^{n}\alpha _{i}\alpha _{j}\langle k(\cdot ,x_{i}),k(\cdot ,x_{j})\rangle_{\mathcal{H}}^2
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \sum _{i,j=1}^{n}\alpha _{i}\alpha _{j}K_{ij}
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \alpha^\intercal K \alpha
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}(y-K\alpha)^\intercal (y-K\alpha)+\frac{\tau}{2} \alpha^\intercal K \alpha
\end{aligned}
\end{equation}

@@

\subsection{Kernel support vector regression}
Support vector regression (SVR) can be kernelized by swapping the $\mathbb{R}^n$ euclidean inner product of $x$ with the inner product in the higher feature space $\mathcal{H}$. Doing so, the optimisation problem can be restated as
\begin{equation}
    \begin{aligned}
        \max_{\lambda_i, \lambda_i^*} \quad& -\frac{1}{2}\sum\limits_{i,j=1}^n(\lambda_i-\lambda_i^*)(\lambda_i-\lambda_i^*)k(x_i, x_j)+\sum\limits_{i=1}^n(y_i-\epsilon)(\lambda_i-\lambda_i^*)
        \\
        s.t. \quad& \sum\limits_{i=1}^n(\lambda_i-\lambda_i^*)=0
        \\
        \quad& \lambda_i, \lambda_i^* \in [0,C]
    \end{aligned}
\end{equation}
Letting $\alpha_i=\lambda_i - \lambda_i^*$, our regressor $f$ is then given by
\begin{equation}
    \begin{aligned}
        f(x)=\sum\limits_{i=1}^n \alpha_i k(x_i, x)+b
    \end{aligned}
\end{equation}
Notice, in this setting $w$ is no longer given explicitly. Additionally, with kernel support vector regression we seek for the flattest function in the feature space instead of the input space.
See Figure \ref{fig:svr2} and Figure \ref{fig:svr3} for two examples. In the former, we have used a polynomial kernel and the standard radial basis function kernel in the latter.
\begin{figure}
    \includegraphics[width=\textwidth]{images/svr2.png}
    \caption{Polynomial support vector regression}
    \label{fig:svr2}
\end{figure}

>>>>

\subsection{Autoregressive integrated moving average with exogenous variables}
The ARIMAX model adds explanatory variables to ARIMA. Hence, we have
\begin{equation}
    \hat{y}_n=\sum\limits_{k=1}^{h} \mu_i X_{n-k}+\sum\limits_{i=1}^{p}\psi_i y_{n-i}^{(d)}+\sum\limits_{j=1}^{q}\theta_j \epsilon_{n-j}+ \epsilon_{n}
\end{equation}
\subsection{Seasonal autoregressive integrated moving average and seasonal autoregressive integrated moving average with exogenous variables}
SARIMA and SARIMAX incorporate seasonalities into time series models. The notation for these models is ARIMA$(p,d,q)(P,D,Q)_m$. The second term $(P,D,Q)_m$ represents the autoregressive structure of the seasonal pattern, where $m$ indicates the number of seasonalities of the time series.
For instance, in modelling series of hourly data with daily periodicity, we would set $m=24$.
Writing SARIMA in compact notation we have
\\
\begin{equation}
    \psi(B)\Psi(B^P)\nabla^d\nabla_m^Dy_t=\theta(B)\Theta(B^Q)\epsilon_t
\end{equation}
where $\Psi$ and $\Theta$ account for the $P$ and $Q$ of the seasonal pattern $m$ respectively.
\section{Generalised additive model}
% in standard regression the predicted y are normal since error are normal. But if we want to model say a y bernoulli which is the rate of success we can link the domain of bernoulli to that of gaussian with a link function
Generalised additive models (GAMs) take the form
\begin{equation}
    g[\mathbb{E}(Y_i)]=\alpha+f_1(X_1)+\dots+f_p(X_p)
\end{equation}
$f_i$ are smooth functions which are fitted using cubic smoothing splines.
Herein, $g$ is called link function and characterizes the specific GAM model \cite{hastie2017generalized}. Approximations for $f_i$ are obtained through an iterative procedure, the backfitting algorithm.

%prophet meta
Particularly successful in time series forecasting is the Prophet model \cite{taylor2018forecasting}, developed by Meta. This additive model is capable of handling non linear trends, holiday effects and yearly weekly, and daily seasonalities. This is, the reason why we choose it as a benchmark to compare against.
\section{K-nearest neighbours regression}
K-nearest neighbours regression forecasts by averaging the most similar $k$ instances in the training set \cite{macqueen1967some}. $k$ is the algorithm hyperparameter, it stands for the number of neighbours; a small $k$ leads to overfitting while a big $k$ leads to underfitting. 
Since it is a metric based algorithm, it is important to normalise data in order to give equal weights to features with different scales, see Appendix \ref{appendix:normalization}.
This algorithm is made up of two decisions: first, the choice of the metric and second, the method for combining targets.

@@

\section{Artificial neural networks}
Artificial neural networks (ANN) have been successfully applied in the context of electricity markets forecasting. The basic building block of this class of methods is the perceptron \cite{rosenblatt1958perceptron}.
This model is defined as follows
\begin{equation}
    y=\psi(wx+b)
\end{equation}
where $\psi$ is an activation function and $w,b$ are the parameters of the neuron. The parameters are typically optimised through gradient descent.

@@

\section{Kernel methods}
\subsection{Kernel ridge regression}
In the setting of kernel ridge regression, we aim at estimating $f$ such that $y=f(x)+\epsilon$. Given an RKHS $\mathcal{H}$, we can estimate $f$ by solving the optmisation problem
\begin{equation}\label{eq:kernel ridge}
    \hat{f}=\argmin{f\in \mathcal{H}}\frac{1}{2}\sum\limits_{i=1}^n(y_i-f(x_i))^2+\frac{\tau}{2}\|f\|_{\mathcal{H}}^2
\end{equation}
Before proceeding, we need to introduce the representer theorem.
\begin{theorem}
    Let $k:\mathcal{X} \times \mathcal{X} \to \mathbb{R}$ on a non empty set $\mathcal{X}$ with corresponding RKHS $\mathcal{H}$,
    a strictly increasing real valued function $g:[0,\infty) \to \mathbb{R}$, and the loss function $E:(\mathcal{X}\times \mathbb{R}^2)^n \to \mathbb{R} \cup \{\infty\}$.
    Consider the regularised risk functional $Risk[f]:f \mapsto  E\left((x_{1},y_{1},f(x_{1})),\ldots, (x_{n},y_{n},f(x_{n}))\right)+g\left(\| f\|_{\mathcal{H}} \right)$. Then any minimiser of the empirical risk can be represented as $$ f^{*}(\cdot )=\sum\limits_{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})$$
\end{theorem}

\begin{proof}
    By orthogonal projection, any $f \in \mathcal{H}$ can be decomposed as the sum of two functions, with the first lying in the $\textrm{span}\{\phi(x_1),\dots, \phi(x_n)\}$ and the second staying in the orthogonal complement of the former. Letting $\nu$ denote a function from the orthogonal complement, we have
    \begin{equation}
        f=\sum\limits_{i=1}^{n}\alpha_i \phi(x_i)+\nu
    \end{equation}
    Applying $f$ to any point, by the reproducing property we have
    \begin{equation}
        \begin{aligned}
            f(x_j)=&\langle \phi(x_j), \sum\limits_{i=1}^{n}\alpha_i \phi(x_i)+\nu\rangle_{\mathcal{H}}
            \\
            =&\sum\limits_{i=1}^{n}\alpha_i\langle \phi(x_j), \phi(x_i)\rangle_{\mathcal{H}}
        \end{aligned}
    \end{equation}
    This means that setting $\nu=0$ does not affect the evaluation of $f$.
    Next consider the regularisation term. The functional $g$ is defined to be strictly monotonic in order to penalise more complex functions $f$.
    \begin{equation}
        \begin{aligned}
            g(\|f\|_{\mathcal{H}})=&g\left(\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)+v\right\|_\mathcal{H}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)+v\right\|_\mathcal{H}^2}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2+\left\|v\right\|_\mathcal{H}^2+2\left\langle\sum\limits_{i=1}^n \alpha_i \phi(x_i),\nu \right\rangle_{\mathcal{H}}}\right)
            \\
            =&g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2+\|v\|_\mathcal{H}^2}\right)
            \\
            \geq &g\left(\sqrt{\left\|\sum\limits_{i=1}^n \alpha_i \phi(x_i)\right\|_{\mathcal{H}}^2}\right)
        \end{aligned}
    \end{equation}
    Hence, we can conclude that setting $\nu=0$ decreases the second term while the first term is not affected. Thus, it follows that any minimiser of the risk functional of Equation \ref{eq:kernel ridge} must be of the following form
    \begin{equation}
        f^*(\cdot)=\sum\limits_{i=1}^n \alpha_i \phi(x_i)=\sum\limits_{i=1}^n \alpha_i k(\cdot, x_i)
    \end{equation}
\end{proof}

Employing the representer theorem, we can rewrite Equation \ref{eq:kernel ridge} in matrix notation as
\begin{equation}
    \begin{aligned}
    \hat{\alpha}=&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2}\left\|\sum _{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})\right\|_{\mathcal{H}}^2
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \left\langle \sum _{i=1}^{n}\alpha _{i}k(\cdot ,x_{i}),\sum _{j=1}^{n}\alpha _{j}k(\cdot ,x_{j})\right\rangle_{\mathcal{H}}
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \sum _{i,j=1}^{n}\alpha _{i}\alpha _{j}\langle k(\cdot ,x_{i}),k(\cdot ,x_{j})\rangle_{\mathcal{H}}
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \sum _{i,j=1}^{n}\alpha _{i}\alpha _{j}K_{ij}
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}\|y-K\alpha\|_2^2+\frac{\tau}{2} \alpha^\intercal K \alpha
    \\
    =&\argmin{\alpha \in \mathbb{R}^n}\frac{1}{2}(y-K\alpha)^\intercal (y-K\alpha)+\frac{\tau}{2} \alpha^\intercal K \alpha
\end{aligned}
\end{equation}

@@

\subsection{Kernel support vector regression}
Support vector regression (SVR) can be kernelized by swapping the $\mathbb{R}^n$ Euclidean inner product of $x$ with the inner product in the higher feature space $\mathcal{H}$. Doing so, the optimisation problem can be restated as
\begin{equation}
    \begin{aligned}
        \max_{\lambda_i, \lambda_i^*} \quad& -\frac{1}{2}\sum\limits_{i,j=1}^n(\lambda_i-\lambda_i^*)(\lambda_i-\lambda_i^*)k(x_i, x_j)+\sum\limits_{i=1}^n(y_i-\epsilon)(\lambda_i-\lambda_i^*)
        \\
        s.t. \quad& \sum\limits_{i=1}^n(\lambda_i-\lambda_i^*)=0
        \\
        \quad& \lambda_i, \lambda_i^* \in [0,C]
    \end{aligned}
\end{equation}
Letting $\alpha_i=\lambda_i - \lambda_i^*$, our regressor $f$ is then given by
\begin{equation}
    \begin{aligned}
        f(x)=\sum\limits_{i=1}^n \alpha_i k(x_i, x)+b
    \end{aligned}
\end{equation}
Notice, in this setting $w$ is no longer given explicitly. Additionally, with kernel support vector regression we seek for the flattest function in the feature space instead of the input space.
See Figure \ref{fig:svr2} and Figure \ref{fig:svr3} for two examples. In the former, we have used a polynomial kernel and the standard radial basis function kernel in the latter.
\begin{figure}
    \includegraphics[width=\textwidth]{images/svr2.png}
    \caption{Polynomial support vector regression}
    \label{fig:svr2}
\end{figure}
